Iterative Reduction: Parsing and Interpreting Code Without Trees

### 2025-02-09 Paper/paper.tex
Fixed single use of type

The initial $\beta$-reducer is a function
\[ \hb \colon \Sigma\times\Sigma \partial \Sigma\times(\bbZ\times\bbZ\to\bbZ)\times(\values\times\values\partial\values) \]
That is, the initial $\beta$-reducer takes two types from $\Sigma$ and returns the following:
\begin{enumerate}
    \item a new \kind,
    \item a function to determine the priority of the new \kind{} given the priorities of the original two \kinds,
    \item and a function to determine the value of the new \kind{} given the values of the original two \kinds.
\end{enumerate}

>>>>

The initial $\beta$-reducer is a function
\[ \hb \colon \Sigma\times\Sigma \partial \Sigma\times(\bbZ\times\bbZ\to\bbZ)\times(\values\times\values\partial\values) \]
That is, the initial $\beta$-reducer takes two \kinds{} from $\Sigma$ and returns the following:
\begin{enumerate}
    \item a new \kind,
    \item a function to determine the priority of the new \kind{} given the priorities of the original two \kinds,
    \item and a function to determine the value of the new \kind{} given the values of the original two \kinds.
\end{enumerate}
